Association between Breast Cancer and Hepatitis C Virus with Age Controlling

### 2022-11-14 manuscript/manuscript.tex
intro

Specifically, this paper will determine if there is an association between testing positive for hepatitis C virus
and breast cancer while controlling for age in Egyptian populations. Both Hepatitis C and breast 
cancer are extremely prevalent in Egypt \citep{Hussein2021high}. Very recently on October 6th, 
Egypt and Qatar agreed to collaborate in the health sector and use each 
other's expertise. The health ministers specifically mentioned research in Hepatitis C and breast cancer
as a area of interest \citep{arham2022egypt}. Thus, research surrounding these diseases is becoming more
important in the field.

@@

2x2 Contingency Table for all patients:

@@

@@

\section{Application}
\label{sec:app}
-

\section{Discussion}
\label{sec:discuss}

-

>>>>

Specifically, this paper will examine if there is an association between 
testing positive for hepatitis C virus and breast cancer while controlling 
for age in Egyptian populations. Both Hepatitis C and breast 
cancer are extremely prevalent in Egypt \citep{Hussein2021high}.
Additionally, research has found that women who are seropositive for 
HCV have more agressive forms of breast cancer. However, there is 
minimal research concerning the effect of age on the associaiton.

Recently on October 6th, Egypt and Qatar agreed to collaborate in the health sector and use each 
other's expertise. The health ministers specifically mentioned research 
in Hepatitis C and breast cancer as an area of interest \citep{arham2022egypt}. 
This meeting emphasizes the importance of diving into Hepatitus C Virus 
and it's association with breast cancer. There have been conflicting
foundings so studies should indenify additional variables that could 
contribute to better understanding the relationship. For that reason,
this paper is focusing on controlling for age of female patients.

@@

\begin{minipage}{\textwidth}
2x2 Contingency Table for all patients:

@@

\end{minipage}

@@

\section{Application}
\label{sec:app}
Fisher's exact test for the pooled data of all patients tested 
\[
H_{0}:p_{1}=p_{2}, H_{a}:p_{1}>p_{2}
\]
at a 0.05 level of confidence.

The test resulted in a p-value of 0.0027, which is less than 
alpha = 0.05. Thus, the null hypothesis is rejected and there 
is evidence suggesting patients who are seropositive have a
higher breast cancer rate than those who are seronegative.

Next, the Breslow Day test checks for homogeneity between the 
stratified ages. 
\[
H_{0}:OR_{1}=OR_{2}, H_{a}:OR_{1}\neq{OR_{2}}
\]
at a 0.01 level of confidence.

The test resulted in a p-value of 0.0133, which is greater than
the alpha value. Thus, we can conclude the strata have similar
odds ratios and proceed with the Mantel-Haenszel procedure.

The Mantel-Haenszel test produced a common odds ratio of 1.6847 and 
a 95 percent confidence interval of (0.9283, 3.0574). The interval
contains 1 so after controlling for age, the association is not supported.

However, the individual odds ratios for age groups are worth noting. For 
the older group (45 and older) the odds ratio estimate and interval are 
1.0290 and (0.5197, 2.0374). The odds ratio estimate and interval for the 
younger group (less than 45) are 7.0318 and (1.5828, 31.2399). Therefore,
the association between seropositivity and breast cancer is much stronger
for females less than 45 years.

\section{Discussion}
\label{sec:discuss}
Based on the
